\clearpage
\section*{Appendix A: Stimuli used for Experiments 1-3}
\renewcommand{\baselinestretch}{1.5}
Stimuli are shown in transitive frame. In the ditransitive light verb construction, the underlined verb would serve as the light noun, i.e., \emph{After their first date, Douglas kissed Mary} $\rightarrow$ \emph{After their first date, Douglas gave a kiss to Mary}.
\emph{
\begin{enumerate}
\item \textup{Punctive Count }
\begin{enumerate}
\item After their first date, Douglas \underline{kissed} Mary.
\item Laughing nastily, the thug \underline{kicked} the victim.
\item When they met up, Nathasha \underline{hugged} Cynthia.
\item Noam \underline{embraced} Jennifer before they split up.
\item Julius \underline{cuddled} his brother at bedtime.
\item Laura \underline{poked} Owen because he was so annoying.
\item Martin \underline{shook} the cocktail before he served it.
\end{enumerate}
\item \textup{Durative Count}
\begin{enumerate}
\item The professor \underline{lectured} on injustice yesterday.
\item The CEO \underline{talked} about his latest sales strategy last night.
\item The President \underline{spoke} about affordable education on Wednesday.
\item During the community art show, the composer \underline{presented} his latest work.
\item After the graduation ceremony, Tom Hanks \underline{addressed} the students.
\item The mother \underline{scolded} the child today.
\end{enumerate}
\item \textup{Durative Mass}
\begin{enumerate}
\item The professor \underline{advised} her student on his paper yesterday.
\item Yesterday, the nurse \underline{assisted} Dr. Kohler in the emergency room.
\item After the job interview, Sheila \underline{assured} Keith.
\item Before Kelly left for a year abroad, her friends \underline{encouraged} her.
\item After the devastating flood, the mayor \underline{recognized} the rescue workers.
\item His new girlfriend \underline{supported} Sam after his divorce.
\item At the summer party, the university official \underline{thanked} the academic community for their efforts.
\end{enumerate}
\end{enumerate}
}

